---
title: "WMO Analysis"
author: "Theodros H."
date: "3/6/2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
#EXCLUDED 625
WMO Analysis
There are 8 blocks of set size 3 trials and 6 blocks of set size 6 trials per participant for a total of 14 blocks
```{r}
#start up
rm(list = ls())
library(matlab)


```
Import data and set variables
```{r}

# <- "/Volumes/GoogleDrive/My Drive/CCDL Shared/Shared/Teddy/winter_19_subjectpool_data/"
#setwd('/Volumes/GoogleDrive/My Drive/CCDL Shared/Shared/Teddy/winter_19_subjectpool_data')

#Import data
wmodata <- read_delim('./processed_wmo/wmo_training_uclimb_and_subjectpool.txt') 
wmotestdata<- read_delim('./processed_wmo/wmo_test_uclimb_and_subjectpool.txt') 
#wmodata <- read.csv('./Processed/wmo_trainingAllParticipants.txt') 
Training.blocks <- c(3,6,3,3,6,3,6,6,3,3,6,3,6,3) #from data
block.3 <- which(Training.blocks==3)
block.6 <- which(Training.blocks==6)
#logical indices
ns3 <- wmodata$trial==39
ns6 <- wmodata$trial==78
#variable declaration as determined by saved data
wmo.N.trials <- 780 
ns3.blks <- 8 
ns6.blks <- 6
ns3.n <- 3
ns6.n <- 6
#maintain a universal list of participants
#Subs <- unique(wmodata$subject)#this will change

Subjects <- as.matrix(read.csv(
  paste(dataPath,"winter19STAGSubjects.csv",sep = ""),
  header = FALSE))

```
 
This block performs the learning/acuracy curve: acc by item iteration
```{r, echo=FALSE}
i=1
mean.acc.3 <- c()
mean.acc.6 <- c() 
wmo.s <- c()

#iterate through each subject here:
for (s in Subjects) {
OneSub <- wmodata$subject==s  
if(any(OneSub)){

#rehsape script here: this reshapes response vector in to trial x block
#use these to find the trials
temp.sort.3 <- reshape(as.matrix(wmodata$seq[OneSub & ns3]),39,ns3.blks)
temp.sort.6 <- reshape(as.matrix(wmodata$seq[OneSub & ns6]),78,ns6.blks)
#these are the actual data. 
temp.dat.3 <- reshape(as.matrix(wmodata$acc[OneSub & ns3]),39,ns3.blks)
temp.dat.6 <- reshape(as.matrix(wmodata$acc[OneSub & ns6]),78,ns6.blks)
#iterate through blocks here:
temp.cat.3 <- c()
temp.cat.6 <- c()

for (n in 1:ns3.blks) {
  #iterate through items here
 #temp.cat.3<- cbind(temp.cat.3,reshape(as.matrix(sort(temp.sort.3[,n])),13,3)) #accumulates across blocks
 
  temp.cat.3<-cbind(temp.cat.3,cbind(as.matrix(temp.dat.3[temp.sort.3[,n]==1,n][1:12]),
                                     as.matrix(temp.dat.3[temp.sort.3[,n]==2,n][1:12]),
                                      as.matrix(temp.dat.3[temp.sort.3[,n]==3,n][1:12])
                                     )
                    )
   if(TRUE){ 
     if (n <= ns6.blks) {
          temp.cat.6<-cbind(temp.cat.6,cbind(as.matrix(temp.dat.6[temp.sort.6[,n]==1,n][1:12]),
                                      as.matrix(temp.dat.6[temp.sort.6[,n]==2,n][1:12]),
                                      as.matrix(temp.dat.6[temp.sort.6[,n]==3,n][1:12]),
                                      as.matrix(temp.dat.6[temp.sort.6[,n]==4,n][1:12]),
                                      as.matrix(temp.dat.6[temp.sort.6[,n]==5,n][1:12]),
                                      as.matrix(temp.dat.6[temp.sort.6[,n]==6,n][1:12])
                                     )
          )
          }
     }
 
} 
#clean missing values -1 
temp.cat.6[temp.cat.6==-1]=0
temp.cat.3[temp.cat.3==-1]=0
#save subject
wmo.s[i] <- s
i = i+ 1

 mean.acc.3 <-cbind(mean.acc.3,rowMeans(temp.cat.3,na.rm = FALSE)) # accumulates across subjects
 mean.acc.6 <-cbind(mean.acc.6,rowMeans(temp.cat.6,na.rm = TRUE))
 #print(length(rowMeans(temp.cat.6,na.rm = TRUE)))
 plot(rowMeans(temp.cat.3),ylim = c(0,1),col = 'green4',
      cex=1,lwd=2,pch=19, xlab ='Stimulus Iteration number',
      ylab ='Accuracy', main = s)
lines(rowMeans(temp.cat.3),ylim = c(0,1),col = 'green4',lwd=2)
points(rowMeans(temp.cat.6),ylim = c(0,1),col = 'orange',pch=19,cex=1,lwd=2)
lines(rowMeans(temp.cat.6),ylim = c(0,1),col = 'orange',lwd=2)
legend("bottomright", c("set size 3", "set size 6"),pch = c( 19, 19),
       text.col =c( "green4","orange"), col = c("green4","orange"))
}
else {
  #use this to track missing data
  wmo.s <-cbind(wmo.s,s) 
  
mean.acc.3 <-cbind(mean.acc.3,rep(NA,12)) # accumulates across subjects
mean.acc.6 <-cbind(mean.acc.6,rep(NA,12))
}
}
# set size 3 vs set size 6 performance indicator: subtract the two and take the average for each iteration point. A negative number indicates better performance, overall in set size 6, no difference if close to zero
wmo.learn.score <- colMeans(mean.acc.3-mean.acc.6)

```

```{r}

#fit curves
wmons3<- data.frame("Y"=rowMeans(mean.acc.3,na.rm = TRUE),"x"=1:12)
wmons6<- data.frame("Y"=rowMeans(mean.acc.6,na.rm = TRUE),"x"=1:12)

#wmo.lin.fit<- lm(Y~ x,data = wmoTesting)
wmo.poly.fit.n3<- lm(Y~ poly(x,3),data = wmons3)
wmo.poly.fit.n6<- lm(Y~ poly(x,3),data = wmons6)

#Plot group means and curves
 plot(rowMeans(mean.acc.3,na.rm = TRUE),ylim = c(0,1),col = 'green4',
      cex=1,lwd=2,pch=19, xlab ='Stimulus Iteration number',
      ylab ='Accuracy' ,main = 'Group Means')
 #lines(rowMeans(mean.acc.3),ylim = c(0,1),col = 'green4',lwd=2)
points(rowMeans(mean.acc.6),ylim = c(0,1),col = 'orange',pch=19,cex=1,lwd=2)
#lines(rowMeans(mean.acc.6),ylim = c(0,1),col = 'orange',lwd=2)
legend("bottomright", c("set size 3", "set size 6"),pch = c( 19, 19),
       text.col =c( "green4","orange"), col = c("green4","orange"))

lines(wmons3$x,wmo.poly.fit.n3$fitted.values,lwd=2.3, col = 'green')
lines(wmons6$x,wmo.poly.fit.n6$fitted.values,lwd=2.3, col = 'red')

#abline(reg = wmo.lin.fit)

#draw error bars
#arrows(1:12, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)
```

Plot group performance on learning and test: box plots.
```{r}
#compute accuracy in testing
ns3.test.mean <- c()
ns6.test.mean <- c()
i = 1
for (s in Subjects) {
  OneSub <- wmotestdata$subject==s  
  ns3.test.mean[i] <- mean(wmotestdata[!is.na(match(wmotestdata[,"stim"],block.3)) & OneSub,"acc"])
  ns6.test.mean[i] <- mean(wmotestdata[!is.na(match(wmotestdata[,"stim"],block.6)) & OneSub,"acc"])

  i = i + 1
}
TestData=data.frame  (ns3.test.mean,ns6.test.mean)
#plot
TestData

#ggplot(data = TestData, aes(y= TestData)) + geom_boxplot()
```

```{r Learn_metric}
ns3.learn <- colMeans(mean.acc.3[6:12, ])
ns6.learn <- colMeans(mean.acc.6[6:12, ])

learn_metric <- (ns3.learn - ns3.test.mean) - (ns6.learn - ns6.test.mean)

```

```{r saveData}
RLWM_data <-  data.frame("subject" = wmo.s,
                         "train_3_acc" = colMeans(mean.acc.3),
                         "train_6_acc" = colMeans(mean.acc.6),
                         "test_3_acc"  = ns3.test.mean,
                         "test_6_acc"  = ns6.test.mean,
                         "learnDiff"   = wmo.learn.score 
  )
write.csv(RLWM_data, "./processed/RLWM_results_winter_subjects.csv")
```
Correlation with test for ns6
For a person with a large WM capacity- ns6 curve will be driven up early (higher accuracy at eariler iterations), smaller difference in areas between the two curves, and according to Collins, a negative correlation between accuracy on ns6 test and AUC of ns6 training. 